---
title: Project Title
format:
  poster-typst: 
    size: "33x23" # Approximately A1
    poster-authors: "Oh Jia Wei, Darien, Peter Febrianto Afandy, Quek Joo Wee, Desmond Loy Yong Kiat, Rene Low Yi Xuan, Phileo Teo Weihan"
    departments: "SIT-UoG Computing Science"
    institution-logo: "./images/sit-logo.png"
    footer-text: "CSC3107 Project (Team Oldlace)"
    footer-emails: "2200607, 2200959, 2201046, 2201435, 2202620, 2203179"
execute:
  echo: false
knitr:
  opts_chunk:
    dev: svglite
---

```{r}
#| label: setup
#| include: false

# Execute data preparations and load graphics
# library(knitr)
# purl("../preparation/preparation.qmd")
# source("../preparation/preparation.R")
```


# Introduction
...

# Previous Visualization
...

# Strengths
*  ...
*  ...

# Suggested Improvements
1. ...
2. ...
    
    
# Implementation
## Data
*  ...
*  ...



## Software
We used the Quarto publication framework and the R programming language, along with the following third-party packages:

*   *readxl* for data import
*   *tidyverse* for data transformation, including *ggplot2* for visualization
    based on the grammar of graphics
*   *knitr* for dynamic document generation

# Improved Visualization
...
```{r}
#| label: fig-ggplot
# Some code here
```


# Further Suggestions for Interactivity
...

# Conclusion
...
